### 2021-06-08 paper/report.tex
Add footnote on our vaccination effectiveness decision.

The model includes several other features, which are crucial to describe the evolution
of the pandemic in 2020-2021. New virus strains with different profiles regarding
infectiousness and disease progress can be introduced. With a probability calibrated to
\cite{Hunter2021}, vaccinated agents become immune and they do not transmit the virus
\citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}.
% the sources only report reduced viral shedding and reduced risk of infection.
% Lauterbach calculated that taking the risk of infection * reduced infectiousness given
% infection based on theses studies suggest that given exposure the risk that fully
% vaccinated individuals pose is <10% of an unvaccinated person.
While vaccines are rolled out, priority may depend on age and occupation. Agents may
demand two types of tests as described in Figure~\ref{fig:pcr_antigen_tests}. First,
polymerase chain reaction (PCR) tests directly reveal whether an individual is infected
or not. PCR tests require some time to be processed and there are always aggregate
capacity constraints. Second, rapid antigen tests yield immediate results. Specificity
and sensitivity of these tests is set according to data by \cite{Bruemmer2021,
Smith2021} . The sensitivity of the rapid antigen tests depends on the timing of the
test relative to the start of infectiousness.\comment[id=HM]{subsequent PCR tests,
quarantine, work/school}. Demand for rapid tests will depend on policy, e.g., prices,
testing requirements before work, attending school, or visiting restaurants and shops.

>>>>

The model includes several other features, which are crucial to describe the evolution of
the pandemic in 2020-2021. New virus strains with different profiles regarding
infectiousness \replaced[id=K]{and disease progress}{}\comment[id=K]{sid only supports
differing infectiousness between variants at the moment} can be introduced. With a
probability of 75\% \citep{Hunter2021}, vaccinated agents become immune and they do not
transmit the virus \citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}.\footnote{75\%
is lower than what is usually reported for after the second dose. We choose it because in
our model does not include booster shots and does not allow for vaccinated individuals to
become infected and transmit the disease which is the case for Covid-19
\citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}.}% the sources only report reduced viral shedding and reduced risk of infection.
% Lauterbach calculated that taking the risk of infection * reduced infectiousness given
% infection based on theses studies suggest that given exposure the risk that fully
% vaccinated individuals pose is <10% of an unvaccinated person.
While vaccines are rolled out, priority depends on age and occupation. Agents may
demand two types of tests as described in Figure~\ref{fig:pcr_antigen_tests}. First,
polymerase chain reaction (PCR) tests directly reveal whether an individual is infected
or not. PCR tests require some time to be processed and there are always aggregate
capacity constraints. Second, rapid antigen tests yield immediate results. Specificity
and sensitivity of these tests is set according to data by \cite{Bruemmer2021,
Smith2021} . The sensitivity of the rapid antigen tests depends on the timing of the
test relative to the start of infectiousness.\comment[id=HM]{subsequent PCR tests,
quarantine, work/school}. Demand for rapid tests will depend on policy, e.g., prices,
testing requirements before work, attending school, or visiting restaurants and shops.
